### 2008-03-11 trunk/Papers/dl-gre-08/discussion.tex
Whee! Even faster!

In order to get a more comprehensive picture of our system's
efficiency, we ran the two algorithms on random graphs with increasing
numbers of nodes.  \todo{harmonize this with what Carlos calls them in
  Section~\ref{sec:bisim}} Each graph had ten different atoms and four
different roles, a 10\% chance for a node to have each atom, and a
10\% chance for each pair of nodes to be connected by each role.  The
results (averaged over 10 runs for each graph size) are shown in
Fig.~\ref{fig:runtimes}.  As the figure shows, the \el\ algorithm
takes about 400 ms on average to generate relational REs for all
individuals in the graph with 100 nodes, i.e.\ 4 ms on average for
each individual.  The \alc\ algorithm is slower by a constant factor
of about 2-3 which probably reflects implementation differences.  In
both cases, we think we can conclude that the systems are fast enough
for practical use.

>>>>

In order to get a more comprehensive picture of our system's
efficiency, we ran the two algorithms on random graphs with increasing
numbers of nodes.  \todo{harmonize this with what Carlos calls them in
  Section~\ref{sec:bisim}} Each graph had ten different atoms and four
different roles, a 10\% chance for a node to have each atom, and a
10\% chance for each pair of nodes to be connected by each role.  The
results (averaged over 10 runs for each graph size) are shown in
Fig.~\ref{fig:runtimes}.  As the figure shows, the \el\ algorithm
takes about 350 ms on average to generate relational REs for all
individuals in the graph with 100 nodes, i.e.\ 4 ms on average for
each individual.  The \alc\ algorithm is even faster, at about 200 ms
for the graph with 100 nodes.  In both cases, we conclude that the
systems are fast enough for practical use.
